\huge Tor's Usability for Censorship Circumvention

### 2016-05-07 pets2017-paper/pets2017-paper.tex
switch to median times over aggregate times. This is before the bug was fixed for 3 participants; TODO: update the figures.

The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Logs show that participants spent 64\% of their overall time at the progress screen. 
Participants using the new interface and old interface spent approximately the same amount of absolute time on the progress screen (359 minutes versus 339 minutes, respectively). 
Table ~\ref{table:overall_time} shows the percentage of time spent on each screen,
computed by the total number of minutes all participants spent on each screen.

@@

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  5\% & 17\% & 6\% & 0\% & 64\% \\
	E1-NEW & 34\% & 4\% & 6\% & 1\% & 50\% \\
	E1-OLD & 23\% & 35\% & 9\% & N/A & 21\% \\
	E2-NEW & 5\% & 4\% & 4\% & 1\% & 80\% \\
	E2-OLD & 4\% & 22\% & 4\% & N/A & 66\% \\
	E3-NEW & 6\% & 7\% & 4\% & 1\% & 70\% \\
	E3-OLD & 4\% & 25\% & 9\% & N/A & 60\% \\
	\end{tabular}
\caption{Fraction of time spent on each screen, 
computed by the total number of minutes all participants spent on each screen. 
Participants spent most of their time on the progress screen.
Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
although none of the censorship environments required a proxy.
Participants spent less time on the proxy screen
in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
\label{table:overall_time}
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r}
	 & Total Active Minutes & \% of Overall Time \\
	\noalign{\hrule}
	All & 381 & 29\% \\ 
	E1-NEW & 4 & 45\% \\
	E1-OLD & 19 & 67\% \\
	E2-NEW & 15 & 15\% \\
	E2-OLD & 68 & 31\% \\
	E3-NEW & 74 & 18\% \\
	E3-OLD & 200 & 38\% \\
	\end{tabular}
\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
\label{table:active_time}
\end{table}

>>>>

The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Logs show that participants spent 58\% of their overall time at the progress screen. 
{\color {red} discuss by environment (time on first) and by version (proxy).}
Table ~\ref{table:median_time} shows the median percentage of time spent on each screen,
computed independently for each screen.

@@

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	All & 7\% & 5\% & 4\% & 58\% \\
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 6\% & 5\% & 5\% & 80\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 4\% & 3\% & 5\% & 78\% \\
	E3-OLD & 3\% & 11\% & 6\% & 60\% \\
	% (median, total) 
	%All & (7, 5)\% & (5, 17)\% & (4, 6)\% & (58, 64)\% \\
	%E1-NEW & (28, 34)\% & (0, 4)\% & (0, 6)\% & (60, 50)\% \\
	%E1-OLD & (30, 23)\% & (0, 35)\% & (0, 9)\% & (29, 21)\% \\
	%E2-NEW & (6, 5)\% & (5, 4)\% & (5, 4)\% & (80, 80)\% \\
	%E2-OLD & (7, 4)\% & (18, 22)\% & (8, 4)\% & (45, 66)\% \\
	%E3-NEW & (4, 6)\% & (3, 7)\% & (5, 4)\% & (78, 70)\% \\
	%E3-OLD & (3, 4)\% & (11, 25)\% & (6, 9)\% & (60, 60)\% \\
	\end{tabular}
\caption{The median percent of time participants spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage independent for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

%\begin{table}[t]
%\centering
%	\begin{tabular}{c r r r r}
%	& First & Proxy & Bridge & Progress \\
%	\noalign{\hrule}
%	All & 5\% & 17\% & 6\% & 64\% \\
%	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
%	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
%	E2-NEW & 5\% & 4\% & 4\% & 80\% \\
%	E2-OLD & 4\% & 22\% & 4\% & 66\% \\
%	E3-NEW & 6\% & 7\% & 4\% & 70\% \\
%	E3-OLD & 4\% & 25\% & 9\% & 60\% \\
%	\end{tabular}
%\caption{The overall percent of time all participants spent on each screen, computed by
%dividing the aggregate number of time on a screen by the aggregate time on all screens.} 
%\label{table:overall_time}
%\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r}
	 & Total Active Minutes & Total \% of Overall Time \\
	\noalign{\hrule}
	All & 381 & 29\% \\ 
	E1-NEW & 4 & 45\% \\
	E1-OLD & 19 & 67\% \\
	E2-NEW & 15 & 15\% \\
	E2-OLD & 68 & 31\% \\
	E3-NEW & 74 & 18\% \\
	E3-OLD & 200 & 38\% \\
	\end{tabular}
\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
\label{table:active_time}
\end{table}
